---
title: "Daily Connecticut Covid Report"
author: "Andrew F. Griffin"
date: "10/29/2020"
output: html_document
---

```{r US GRAPH, echo=FALSE, message=FALSE, warning=FALSE}
library(dslabs)
library(tidyverse)
library(dplyr)
library(zoo)
library(lubridate)
library(janitor)

library(ggplot2)
library(gghighlight)
library(ggrepel)
library(ggthemes)
library(RColorBrewer)
library(viridis)
library(paletteer)
library(usmap)
library(grid)
library(gridExtra)

library(gt)
library(markdown)
library(pracma)
# LOAD DATA
load("rda/covid_ct.rda")
load("rda/theme_DataStache.rda")

##### PLOT CHARTS
# NEW CASES
p_new_case <- covid_ct %>%
  ggplot(aes(date, new_cases)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  # INSERT PHASE 3 REOPEN MARKER
  geom_vline(xintercept = ymd(20201008), size = .15, color = "grey40") +
  geom_bar(stat = "identity", fill="blue", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_cases_07da), size = .25, col="blue") +
  ggtitle("Connecticut New Cases Total",
          subtitle = "New Cases Per Day With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(ylim = c(0, max(covid_ct$new_cases_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# NEW TESTS        
p_new_test <- covid_ct %>%
  ggplot(aes(date, new_tests)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="dark green", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_tests_07da), size = .25, col="dark green") +
  ggtitle("Connecticut New Tests Total",
          subtitle = "Tests Per Day With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(ylim = c(0, max(covid_ct$new_tests_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# NEW DEATHS
p_new_deaths <- covid_ct %>%
  ggplot(aes(date, new_deaths)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="dark red", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_deaths_07da), size = .25, col="dark red") +
  ggtitle("Connecticut New Deaths Total",
          subtitle = "Deaths Per Day With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(ylim = c(0, max(covid_ct$new_deaths_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# NEW HOSPITALIZATION
p_new_hosp <- covid_ct %>%
  ggplot(aes(date, new_hosp)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="yellow4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = new_hosp_07da), size = .25, col="yellow4") +
  ggtitle(paste("Connecticut New Hospitalization"),
          subtitle = "Newly Hospitalized Per Day With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(ylim = c(min(covid_ct$new_hosp_07da, na.rm = TRUE) * 1.1, max(covid_ct$new_hosp_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# CURRENT HOSPITALIZATION
p_hosp <- covid_ct %>%
  ggplot(aes(date, current_hosp)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="orange4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = cur_hosp_07da), size = .25, col="orange4") +
  ggtitle(paste("Connecticut New Hospitalization"),
          subtitle = "Currently Hospitalized With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) +
  coord_cartesian(ylim = c(0, max(covid_ct$cur_hosp_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# PERCENT POSITIVE
p_pos <- covid_ct %>%
  ggplot(aes(date, percent_pos)) +
  geom_hline(yintercept=0, col = "grey40", size = .2) +
  geom_bar(stat = "identity", fill="orange4", alpha = .3, size = .1) +
  scale_color_manual(values="light grey") +
  geom_line(aes(y = percent_pos_07da), size = .25, col="orange4") +
  ggtitle(paste("Connecticut Percent Positive"),
          subtitle = "Percent Share Positive With Rolling 7 Day Average") +
  labs(caption = "Created by Andrew F. Griffin \n Covid Data from data.ct.gov") +
  scale_x_date(date_labels = "%b", breaks= "1 month") +
  scale_y_continuous(expand = c(0,0)) + 
  coord_cartesian(ylim = c(0, max(covid_ct$percent_pos_07da, na.rm = TRUE) * 1.1)) +
  theme_DataStache() +
  theme(text = element_text(size = rel(.55)),
        axis.text = element_text(size = rel(.65)),
        plot.caption = element_text(size = rel(.5)))

# GRID ARRANGE PLOTS
grid.arrange(p_new_case, p_new_test, p_hosp, p_new_deaths, p_pos, p_new_hosp, nrow = 2)
```
<br></br>
<br></br>
```{r STATE SUMMARY TABLE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/covid_ct.rda")
load("rda/ind_tylm_date.rda")
load("rda/ind_tdy.rda")

### CT TABLE
covid_ct %>%
  filter(date %in% ind_tylm_date) %>%
  select(date, new_cases, new_tests, new_deaths, current_hosp, new_hosp, percent_pos) %>%
  gt() %>% 
  tab_options(table.font.size = pct(75)) %>%
  ## LABELS STUB / TITLE / SUBTITLE
  tab_header(title = md("**COVID GROWTH IN CONNECTICUT**"),
             subtitle = md("*Today / Yesterday / Last Week / Last Month*")) %>%
  ## RENAMES COLUMNS
  cols_label(date = md("**Date**"), 
             new_cases = md("**New Cases**"),
             new_tests = md("**New Tests**"),
             new_deaths = md("**New Deaths**"),
             current_hosp = md("**Currently Hospitalized**"),
             new_hosp = md("**Newly Hospitalized**"),
             percent_pos = md("**Percent Positive**")) %>%
  ## FORMATS DATA
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  fmt_number(columns =  vars(new_cases,
                             new_tests,
                             new_deaths),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(date))) %>%   
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Covid Data from data.ct.gov*"))
```
<br></br>

Covid Data for `r month(covid_ct$date[1], label = TRUE)` `r day(covid_ct$date[1])`  
New Cases  
Tdy (`r month(covid_ct$date[1], label = TRUE)`-`r day(covid_ct$date[1])`): `r format(covid_ct$new_cases[1], big.mark = ",")` `r ifelse(covid_ct$new_cases[1] == max(covid_ct$new_cases, na.rm = TRUE), "*", "")`  
Yest (`r month(covid_ct$date[covid_ct$date == ind_tdy - 1], label = TRUE)`-`r day(covid_ct$date[covid_ct$date == ind_tdy - 1])`): `r format(covid_ct$new_cases[covid_ct$date == ind_tdy - 1], big.mark = ",")`  
Lst Wk (`r month(covid_ct$date[covid_ct$date == ind_tdy - 7], label = TRUE)`-`r day(covid_ct$date[covid_ct$date == ind_tdy - 7])`): `r format(covid_ct$new_cases[covid_ct$date == ind_tdy - 7], big.mark = ",")`  
<br></br>
New Tests  
T: `r format(covid_ct$new_tests[1], big.mark = ",")` `r ifelse(covid_ct$new_tests[1] == max(covid_ct$new_tests, na.rm = TRUE), "*", "")`  
Y: `r format(covid_ct$new_tests[covid_ct$date == ind_tdy - 1], big.mark = ",")`  
LW: `r format(covid_ct$new_tests[covid_ct$date == ind_tdy - 7], big.mark = ",")`  
<br></br>
Percent Positive  
T: `r round(covid_ct$percent_pos[1]*100, digits = 1)`%  
Y: `r round(covid_ct$percent_pos[covid_ct$date == ind_tdy - 1]*100, digits = 1)`%  
LW: `r round(covid_ct$percent_pos[covid_ct$date == ind_tdy - 7]*100, digits = 1)`%  
<br></br>
New Deaths  
T: `r format(covid_ct$new_deaths[1], big.mark = ",")` `r ifelse(covid_ct$new_deaths[1] == max(covid_ct$new_deaths, na.rm = TRUE), "*", "")`  
Y: `r format(covid_ct$new_deaths[covid_ct$date == ind_tdy - 1], big.mark = ",")`  
LW: `r format(covid_ct$new_deaths[covid_ct$date == ind_tdy - 7], big.mark = ",")`  
* = Record  
<br></br>

Compared to other `r covid_ct$day[1]`'s
```{r DAY OF THE WEEK STATS, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(day == day[1])
```

The Last Time Things were this bad:
```{r CASES TOP 10, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  arrange(desc(new_cases)) %>% slice_head(n=10) %>% select(date, day, new_cases)
```

```{r CASES TOP 10 07DAY AVERAGE, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  arrange(desc(new_cases_07da)) %>% slice_head(n=10) %>% select(date, day, new_cases_07da)
```

```{r CASES, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(new_cases >= covid_ct$new_cases[1]) %>% select(date, new_cases)
```

```{r CASES 07DA, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(new_cases_07da >= covid_ct$new_cases_07da[1]) %>% select(date, new_cases_07da)
```

```{r DEATH, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(new_deaths >= covid_ct$new_deaths[1]) %>% select(date, new_deaths)
```

```{r DEATH 07DA, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(new_deaths_07da >= covid_ct$new_deaths_07da[1]) %>% select(date, new_deaths_07da)
```

```{r HOSP, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(current_hosp >= covid_ct$current_hosp[1]) %>% select(date, current_hosp)
```

```{r NEW HOSP 07DA, echo=FALSE, message=FALSE, warning=FALSE}
covid_ct %>%
  filter(new_hosp_07da >= covid_ct$new_hosp_07da[1]) %>% select(date, new_hosp_07da)
```

```{r STATE GROWTH TABLE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/covid_ct_sum.rda")

### CT TABLE
covid_ct_sum %>%
  gt() %>% 
  tab_options(table.font.size = pct(75)) %>%
  ## LABELS STUB / TITLE / SUBTITLE
  tab_header(title = md("**COVID GROWTH IN CONNECTICUT**"),
             subtitle = md("*Last Seven Days Compared to Last Week*")) %>%
  ## RENAMES COLUMNS
  cols_label(week = md("**Period**"), 
             sum_new_cases = md("**New Cases**"),
             sum_new_tests = md("**New Tests**"),
             sum_new_deaths = md("**New Deaths**"),
             m_hosp = md("**Avg Hospitalized**"),
             sum_new_hosp = md("**New Hospitalizations**"),
             percent_pos = md("**Percent Positive**")) %>%
  ## FORMATS DATA
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  fmt_number(columns =  vars(sum_new_cases,
                             sum_new_tests,
                             sum_new_deaths),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(week))) %>%   
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Covid Data from data.ct.gov*"))
```
<br></br>
```{r COUNTY SUMMARY TABLE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/covid_ct_counties_sum.rda")
load("rda/covid_ct_counties_zone.rda")

### CT TABLE
merge(covid_ct_counties_sum, covid_ct_counties_zone, by = c("county", "sum_cases_percap", "percent_pos")) %>%
  select(county,
         sum_cases_percap,
         sum_hosp_percap,
         sum_tests_percap,
         percent_pos,
         sum_deaths_percap,
         cases_zone,
         percent_zone) %>%
  arrange(desc(sum_cases_percap)) %>%
  gt() %>% 
  tab_options(table.font.size = pct(75)) %>%
  ## LABELS STUB / TITLE / SUBTITLE
  tab_header(title = md("**COVID GROWTH BY COUNTY IN CONNECTICUT**"),
             subtitle = md("*Based on Total Cases Per 100k Over the Last Seven Days*")) %>%
  ## RENAMES COLUMNS
  cols_label(county = md("**County**"), 
             sum_cases_percap = md("**New Cases**"),
             sum_hosp_percap = md("**New Hospitalization**"),
             sum_tests_percap = md("**New Tests**"),
             percent_pos = md("**Percent Positive**"),
             sum_deaths_percap = md("**New Deaths**"),
             cases_zone = md("**Zone by Cases**"),
             percent_zone = md("**Zone by Positives**")) %>%
  ## FORMATS DATA
  fmt_percent(columns = vars(percent_pos),
              decimals = 1) %>%
  cols_align(align = "center") %>%
  fmt_number(columns =  vars(sum_cases_percap,
                             sum_tests_percap,
                             sum_deaths_percap),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),
            locations = cells_body(columns = vars(county))) %>%   
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Covid Data from data.ct.gov*"))
```
<br></br>
```{r TOWN SUMMARY TABLE, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD DATA
load("rda/town_growth_top10.rda")


### CT TOWNS TABLE
town_growth_top10 %>%
  select(town,
         county,
         sum_new_cases,
         sum_new_tests,
         percent_pos,
         sum_new_deaths) %>%
  gt() %>% 
  ## LABELS STUB / TITLE / SUBTITLE
  tab_options(table.font.size = pct(75)) %>%
  tab_header(title = md("**TOP 10% OF TOWNS FOR COVID GROWTH IN CONNECTICUT**"),
             subtitle = md("*Based on Total Cases Over the Last Seven Days*")) %>%
  ## RENAMES COLUMNS
  cols_label(town = md("**Town**"),
             county = md("**County**"),
             sum_new_cases = md("**New Cases**"),                               
             sum_new_tests = md("**New Tests**"),
             percent_pos = md("**Percent Positive**"),
             sum_new_deaths = md("**New Deaths**")) %>%
  ## FORMATS DATA
  fmt_percent(columns = vars(percent_pos),                                   
              decimals = 1) %>%
  cols_align(align = "center") %>%
  fmt_number(columns =  vars(sum_new_cases,
                             sum_new_tests,
                             sum_new_deaths),
             decimals = 0) %>%
  ## BOLD STATES COLUMN
  tab_style(style = list(cell_text(weight = "bold")),                            
            locations = cells_body(columns = vars(town))) %>% 
  ## STRIPING
  opt_row_striping(row_striping = TRUE) %>%                                      
  tab_source_note(source_note = md("*Created by Andrew F. Griffin, Covid Data from data.ct.gov*"))
```
